Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-07-17 STAT-paper-template/APA/fertile.Rnw
added CI software to lit review

\begin{itemize}
\item[1] Use clear separation, labeling, and documentation.
\item[2] Automate processes when possible.
\item[3] Design the data analysis workflow as a sequence of small steps glued together, with
outputs from one step serving as inputs into the next. This is a common suggestion within the computing community, originating as part of the Unix philosophy (Gancarz (2002)).
\end{itemize}

@@

\subsection{R Packages}

@@

@@

\pkg{fertile} addresses these gaps by providing a simple, easy-to-learn reproducibility package that, rather than focusing intensely on a specific area, provides some information about a wide variety of aspects influencing reproducibility. The package also provides flexibility, offering benefits to users at any stage in the data analysis workflow, unlike some other available packages which can only be used before the creation of a new project or after it is finished.

>>>>

\begin{itemize}
\item[1] Use clear separation, labeling, and documentation.
\item[2] Automate processes when possible.
\item[3] Design the data analysis workflow as a sequence of small steps glued together, with
outputs from one step serving as inputs into the next. This is a common suggestion within the computing community, originating as part of the Unix philosophy \cite{unix}.
\end{itemize}

@@

\subsection{R Packages and Other Software}

@@

There are also several development tools external to R that focus on continuous integration and can be configured to address different aspects of reproducibility. \pkg{Wercker}, a command line tool that leverages Docker, enables users to test whether their projects will successfully compile when run on a variety of operating systems without access to the user's local hard drive \cite{wercker}. \pkg{Travis CI} is integrated with GitHub and can be configured to do similar checks on projects hosted in repositories \cite{travis}. \pkg{Circle CI}, another popular continuous integration tool, can also be used to check R code \cite{circle}.

However, while these tools can be useful in some circumstances, they are generalized so as to be useful to the widest audience. As a result, their checks are not designed to be R-specific, which makes these tools sub-optimal for users looking to address reproducibility issues involving features specific to the R programming language, such as package installtion and seed setting.

@@

\pkg{fertile} addresses these gaps by providing a simple, easy-to-learn reproducibility package that, rather than focusing intensely on a specific area, provides some information about a wide variety of aspects influencing reproducibility. The package also provides flexibility, offering benefits to users at any stage in the data analysis workflow, and R-specific features, which address certain aspects of reproducibility that can be missed by external project development software.
